---
title: "Differential Expression Analysis - Recovery 5FU"
author: "Emma M Pfortmiller"
date: "2025-02-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Libraries, warning=FALSE, include=FALSE}
library(edgeR)
library(tidyverse)
library(readr)
library(BiocGenerics)
library(gridExtra)
library(VennDiagram)
library(kableExtra)
library(scales)
library(ggVennDiagram)
library(Cormotif)
library(RColorBrewer)
library(ggpubr)

```

Create the Data Set:

```{r Data Set, include=FALSE}

counts_DE_raw <- read_csv("C:/Users/emmap/RDirectory/Recovery_RNAseq/Recovery_5FU/data/featureCounts_Concat_Matrix_AllSamples_EMP_250210.csv")
#View(counts_DE)

#this dataset comes from the csv I saved of all raw counts for each sample - but for this initial try I would like to remove my biological replicate for now

counts_DE <- as.data.frame(counts_DE) %>% 
        dplyr::select(-"...1") %>% 
        column_to_rownames(var = "ensembl_gene_id") %>% 
        dplyr::select(-(contains("Ind6REP")))

#now I've removed that individual, so I'll filter all counts by rowmeans
#first check the number of variables in the counts file
##I should have 54 samples if not including Ind6REP
dim(counts_DE)
#[1] 78932    54

#now use rowMeans to filter out values with mean < 0 (this means rowMeans > 0 is what I'm left with) for each row/gene in the original file
rowMeans_DE <- rowMeans(counts_DE)
counts_DE_filter <- counts_DE[rowMeans_DE > 0,]
dim(counts_DE_filter)
#[1] 65925    54

#with this I've filtered out 12268 genes from my raw counts dataset

#I'll double check the appearance of the data after filtering and before filtering
boxplot(counts_DE, 
        main = "Recovery DE Unfiltered Counts", 
        xlab = "Conditions", 
        ylab = "Counts",
        ylim = c(-5,40))


boxplot(counts_DE_filter, 
        main = "Recovery DE Filtered Counts", 
        xlab = "Conditions", 
        ylab = "Counts",
        ylim = c(-5,40))

counts_DE_hist_mut <- (t(counts_DE))
counts_DE_fil_hist_mut <- (t(counts_DE_filter))

hist(counts_DE_hist_mut, main = "Histogram of Raw Counts", ylim = c(-100, 6000000), xlab = "counts", ylab = "Frequency", xlim = c(-1000,150000))

hist(counts_DE_fil_hist_mut, main = "Histogram of Filtered Counts", ylim = c(-100, 6000000), xlab = "counts", ylab = "Frequency", xlim = c(-1000,150000))


#now I'll save this dataset as a csv
#write.csv(counts_DE_filter,  "C:/Users/emmap/RDirectory/Recovery_RNAseq/Recovery_5FU/data/Counts_Matrix_DE_filtered_EMP_250217.csv")

```


Now that I've confirmed that the filtering looks good, let's continue on with the pipeline for DE
```{r Create DGE List Object}

de_list <- DGEList(counts_DE_filter)
de_list_genes <- DGEList(counts_DE_filter, genes = genes)

#I want to include the genes information, so I'll call that column alone to be its own list
genes <- counts_DE_filter %>% rownames_to_column(var = "ensembl_gene_id") %>% dplyr::select("ensembl_gene_id")

```


Now that I've made my DGElist object, let's calculate normalization factors
#calcNormFactors doesn’t normalize the data, it just calculates normalization factors for use downstream#
```{r Normalization Factors Calculation}

#this is the inital file before norm factors are calculated
de_list_genes$samples

#calculate the normalization factors with method TMM
de_list_genes_calc <- calcNormFactors(de_list_genes, method = "TMM")

#final file after norm calculation
de_list_genes_calc$samples

#View(de_list_genes_calc)

```

Now I'll look at the factors I have and pull those out
- Time
- Treatment
- Individual
```{r Pull Out Factors}

snames <- data.frame("samples" = colnames(de_list_genes_calc)) %>% separate_wider_delim(., cols = samples, names = c("Treatment", "Time", "Individual"), delim = "_", cols_remove = FALSE)

#snames_list <- as.list(snames)

snames_time <- snames$Time
snames_tx <- snames$Treatment
snames_ind <- snames$Individual


#define colors for each of these factors
#time colors - have 3 timepoints
time_col <- list(Time = c("24hr" = "#046A38", "24rec" = "#0050B5", "144rec" = "#B3831B"))
#treatment colors - have 3 treatments
tx_col <- list(Treatment = c("DMSO" = "#63666D","5FU" = "#DCACED","DOX" = "#499FBD"))
#individual colors - have 6 individual not including rep at this time
ind_col <- list(Individual = c("Ind1" = "#003F5C", "Ind2" = "#45AE91", "Ind3" =  "#58508D", "Ind4" = "#BC4099", "Ind5" =  "#FF6361", "Ind6" = "#FF2362"))
#all colors together 
all_col <- list(time_col, tx_col, ind_col)

#create a new variable that groups these factors all together
group2 <- interaction(snames_tx, snames_time)
group3 <- interaction(snames_tx, snames_time, snames_ind)

```

```{r Multi-dimensional Scaling Plot (MDS)}

plotMDS(de_list_genes_calc, col = as.numeric(group2))

plotMDS(de_list_genes_calc, col = as.numeric(group3))

```

Now that I've put my matrix together, we can start with Voom transformation and linear modeling
#this specifies a model where each coefficient corresponds to a group mean
```{r Voom Transformation and Linear Modeling}
#put together your model
model_all <- model.matrix(~0 + group3)
model_all

####Voom####

y <- voom(de_list, model_all, plot = T)
```

