---
title: "5FU Project DRC Boxplots Time 78-1, 75-1, 17-3"
author: "Emma M Pfortmiller"
date: "2024-02-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Include these libraries: (these are not from the boxplot thing but I think these are right)

```{r Libraries}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(scales)
```

```{r Excel Sheet} 
library(readxl)
fluo_drc_allind <- read_excel("C:/Users/emmap/RDirectory/5FUProj_DRCTime_78-1_75-1_17-3_EMP_240226.xlsx", 
    sheet = "Raw Data All Lines")
View(fluo_drc_allind)
```

Filter through the data to make sure you have the correct parameters:
1. Sort by DRUG name
2. Sort by timepoint (since they're being treated as separate experiments by time)
```{r Filtering Data 78-1}
fluo_drc_allind

####filter data####
doxosamplesall <- fluo_drc_allind %>% filter(Drug =="DOXO")
doxo24hrall <- doxosamplesall %>% filter(FinTime == "24hr")
doxo48hrall <- doxosamplesall %>% filter(FinTime == "48hr")
doxo72hrall <- doxosamplesall %>% filter(FinTime == "72hr")

fluosamplesall <- fluo_drc_allind %>% filter(Drug =="FLUO")
fluo24hrall <- fluosamplesall %>% filter(FinTime == "24hr")
fluo48hrall <- fluosamplesall %>% filter(FinTime == "48hr")
fluo72hrall <- fluosamplesall %>% filter(FinTime == "72hr")

dmsosamplesall <- fluo_drc_allind %>% filter(Drug =="DMSO")
dmso24hrall <- dmsosamplesall %>% filter(FinTime == "24hr")
dmso48hrall <- dmsosamplesall %>% filter(FinTime == "48hr")
dmso72hrall <- dmsosamplesall %>% filter(FinTime == "72hr")
```

All of the individuals are in the previous dataset together by drug and time
Now separate them out to make individual plots

```{r Separating Out Individuals}
#doxosamples

doxosamples78 <- doxosamplesall %>% dplyr::select("Drug", "Conc", "Well", "Row", "Column", "Plate", "FinTime", "RFLU0_78", "RFLUFin_78")

doxosamples75 <- doxosamplesall %>% dplyr::select("Drug", "Conc", "Well", "Row", "Column", "Plate", "FinTime", "RFLU0_75", "RFLUFin_75")

doxosamples17 <- doxosamplesall %>% dplyr::select("Drug", "Conc", "Well", "Row", "Column", "Plate", "FinTime", "RFLU0_17", "RFLUFin_17")

#fluosamples

fluosamples78 <- fluosamplesall %>% dplyr::select("Drug", "Conc", "Well", "Row", "Column", "Plate", "FinTime", "RFLU0_78", "RFLUFin_78")

fluosamples75 <- fluosamplesall %>% dplyr::select("Drug", "Conc", "Well", "Row", "Column", "Plate", "FinTime", "RFLU0_75", "RFLUFin_75")

fluosamples17 <- fluosamplesall %>% dplyr::select("Drug", "Conc", "Well", "Row", "Column", "Plate", "FinTime", "RFLU0_17", "RFLUFin_17")

#dmsosamples

dmsosamples78 <- dmsosamplesall %>% dplyr::select("Drug", "Conc", "Well", "Row", "Column", "Plate", "FinTime", "RFLU0_78", "RFLUFin_78")

dmsosamples75 <- dmsosamplesall %>% dplyr::select("Drug", "Conc", "Well", "Row", "Column", "Plate", "FinTime", "RFLU0_75", "RFLUFin_75")

dmsosamples17 <- dmsosamplesall %>% dplyr::select("Drug", "Conc", "Well", "Row", "Column", "Plate", "FinTime", "RFLU0_17", "RFLUFin_17")

```

Now that these are separated by individual, I can do some data processing to get some graphs!
Want to compare across individuals, can I plot them on the same graphs?

```{r Filtering By Time}

#doxosamples

doxo24hr78 <- doxosamples78 %>% filter(FinTime == "24hr")
doxo48hr78 <- doxosamples78 %>% filter(FinTime == "48hr")
doxo72hr78 <- doxosamples78 %>% filter(FinTime == "72hr")

doxo24hr75 <- doxosamples75 %>% filter(FinTime == "24hr")
doxo48hr75 <- doxosamples75 %>% filter(FinTime == "48hr")
doxo72hr75 <- doxosamples75 %>% filter(FinTime == "72hr")

doxo24hr17 <- doxosamples17 %>% filter(FinTime == "24hr")
doxo48hr17 <- doxosamples17 %>% filter(FinTime == "48hr")
doxo72hr17 <- doxosamples17 %>% filter(FinTime == "72hr")

#fluosamples

fluo24hr78 <- fluosamples78 %>% filter(FinTime == "24hr")
fluo48hr78 <- fluosamples78 %>% filter(FinTime == "48hr")
fluo72hr78 <- fluosamples78 %>% filter(FinTime == "72hr")

fluo24hr75 <- fluosamples75 %>% filter(FinTime == "24hr")
fluo48hr75 <- fluosamples75 %>% filter(FinTime == "48hr")
fluo72hr75 <- fluosamples75 %>% filter(FinTime == "72hr")

fluo24hr17 <- fluosamples17 %>% filter(FinTime == "24hr")
fluo48hr17 <- fluosamples17 %>% filter(FinTime == "48hr")
fluo72hr17 <- fluosamples17 %>% filter(FinTime == "72hr")

#dmsosamples

dmso24hr78 <- dmsosamples78 %>% filter(FinTime == "24hr")
dmso48hr78 <- dmsosamples78 %>% filter(FinTime == "48hr")
dmso72hr78 <- dmsosamples78 %>% filter(FinTime == "72hr")

dmso24hr75 <- dmsosamples75 %>% filter(FinTime == "24hr")
dmso48hr75 <- dmsosamples75 %>% filter(FinTime == "48hr")
dmso72hr75 <- dmsosamples75 %>% filter(FinTime == "72hr")

dmso24hr17 <- dmsosamples17 %>% filter(FinTime == "24hr")
dmso48hr17 <- dmsosamples17 %>% filter(FinTime == "48hr")
dmso72hr17 <- dmsosamples17 %>% filter(FinTime == "72hr")

```

Now that these are broken up by timepoints, I can graph them all  together

```{r Boxplots DOXORUBICIN ALL INDIVIDUALS}
#DOXO 78-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 5FU Project 78-1",cex = 2,font = 2)

boxplot(doxo24hr78$RFLU0_78 ~ doxo24hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1"
)

boxplot(doxo24hr78$RFLUFin_78 ~ doxo24hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 78-1"
)

#DOXO 75-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 5FU Project 75-1",cex = 2,font = 2)

boxplot(doxo24hr75$RFLU0_75 ~ doxo24hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1"
)

boxplot(doxo24hr75$RFLUFin_75 ~ doxo24hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 75-1"
)

#DOXO 17-3 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 5FU Project 17-3",cex = 2,font = 2)

boxplot(doxo24hr17$RFLU0_17 ~ doxo24hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3"
)

boxplot(doxo24hr17$RFLUFin_17 ~ doxo24hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 17-3"
)

#DOXO 78-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 5FU Project 78-1",cex = 2,font = 2)

boxplot(doxo48hr78$RFLU0_78 ~ doxo48hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1"
)

boxplot(doxo48hr78$RFLUFin_78 ~ doxo48hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 78-1"
)

#DOXO 75-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 5FU Project 75-1",cex = 2,font = 2)

boxplot(doxo48hr75$RFLU0_75 ~ doxo48hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1"
)

boxplot(doxo48hr75$RFLUFin_75 ~ doxo48hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 75-1"
)

#DOXO 17-3 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 5FU Project 17-3",cex = 2,font = 2)

boxplot(doxo48hr17$RFLU0_17 ~ doxo48hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3"
)

boxplot(doxo48hr17$RFLUFin_17 ~ doxo48hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 17-3"
)

#DOXO 78-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 5FU Project 78-1",cex = 2,font = 2)

boxplot(doxo72hr78$RFLU0_78 ~ doxo72hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1"
)

boxplot(doxo72hr78$RFLUFin_78 ~ doxo72hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 78-1"
)

#DOXO 75-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 5FU Project 75-1",cex = 2,font = 2)

boxplot(doxo72hr75$RFLU0_75 ~ doxo72hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1"
)

boxplot(doxo72hr75$RFLUFin_75 ~ doxo72hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 75-1"
)

#DOXO 17-3 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 5FU Project 17-3",cex = 2,font = 2)

boxplot(doxo72hr17$RFLU0_17 ~ doxo72hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3"
)

boxplot(doxo72hr17$RFLUFin_17 ~ doxo72hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 17-3"
)

```

```{r Boxplots 5-FLUOROURACIL ALL INDIVIDUALS}
#FLUO 78-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration FLUO - 5FU Project 78-1",cex = 2,font = 2)

boxplot(fluo24hr78$RFLU0_78 ~ fluo24hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 78-1"
)

boxplot(fluo24hr78$RFLUFin_78 ~ fluo24hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 24hr 78-1"
)

#FLUO 75-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration FLUO - 5FU Project 75-1",cex = 2,font = 2)

boxplot(fluo24hr75$RFLU0_75 ~ fluo24hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 75-1"
)

boxplot(fluo24hr75$RFLUFin_75 ~ fluo24hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 24hr 75-1"
)

#FLUO 17-3 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration FLUO - 5FU Project 17-3",cex = 2,font = 2)

boxplot(fluo24hr17$RFLU0_17 ~ fluo24hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 17-3"
)

boxplot(fluo24hr17$RFLUFin_17 ~ fluo24hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 24hr 17-3"
)

#FLUO 78-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration FLUO - 5FU Project 78-1",cex = 2,font = 2)

boxplot(fluo48hr78$RFLU0_78 ~ fluo48hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 78-1"
)

boxplot(fluo48hr78$RFLUFin_78 ~ fluo48hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 48hr 78-1"
)

#FLUO 75-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration FLUO - 5FU Project 75-1",cex = 2,font = 2)

boxplot(fluo48hr75$RFLU0_75 ~ fluo48hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 75-1"
)

boxplot(fluo48hr75$RFLUFin_75 ~ fluo48hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 48hr 75-1"
)

#FLUO 17-3 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration FLUO - 5FU Project 17-3",cex = 2,font = 2)

boxplot(fluo48hr17$RFLU0_17 ~ fluo48hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 17-3"
)

boxplot(fluo48hr17$RFLUFin_17 ~ fluo48hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 48hr 17-3"
)

#FLUO 78-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration FLUO - 5FU Project 78-1",cex = 2,font = 2)

boxplot(fluo72hr78$RFLU0_78 ~ fluo72hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 78-1"
)

boxplot(fluo72hr78$RFLUFin_78 ~ fluo72hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 72hr 78-1"
)

#FLUO 75-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration FLUO - 5FU Project 75-1",cex = 2,font = 2)

boxplot(fluo72hr75$RFLU0_75 ~ fluo72hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 75-1"
)

boxplot(fluo72hr75$RFLUFin_75 ~ fluo72hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 72hr 75-1"
)

#FLUO 17-3 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration FLUO - 5FU Project 17-3",cex = 2,font = 2)

boxplot(fluo72hr17$RFLU0_17 ~ fluo72hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 17-3"
)

boxplot(fluo72hr17$RFLUFin_17 ~ fluo72hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 72hr 17-3"
)
```

```{r DMSO BOXPLOTS ALL INDIVIDUALS}
#DMSO 78-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 5FU Project 78-1",cex = 2,font = 2)

boxplot(dmso24hr78$RFLU0_78 ~ dmso24hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1"
)

boxplot(dmso24hr78$RFLUFin_78 ~ dmso24hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 78-1"
)

#DMSO 75-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 5FU Project 75-1",cex = 2,font = 2)

boxplot(dmso24hr75$RFLU0_75 ~ dmso24hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1"
)

boxplot(dmso24hr75$RFLUFin_75 ~ dmso24hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 75-1"
)

#DMSO 17-3 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 5FU Project 17-3",cex = 2,font = 2)

boxplot(dmso24hr17$RFLU0_17 ~ dmso24hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3"
)

boxplot(dmso24hr17$RFLUFin_17 ~ dmso24hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 17-3"
)

#DMSO 78-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 5FU Project 78-1",cex = 2,font = 2)

boxplot(dmso48hr78$RFLU0_78 ~ dmso48hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1"
)

boxplot(dmso48hr78$RFLUFin_78 ~ dmso48hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 78-1"
)

#DMSO 75-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 5FU Project 75-1",cex = 2,font = 2)

boxplot(dmso48hr75$RFLU0_75 ~ dmso48hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1"
)

boxplot(dmso48hr75$RFLUFin_75 ~ dmso48hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 75-1"
)

#DMSO 17-3 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 5FU Project 17-3",cex = 2,font = 2)

boxplot(dmso48hr17$RFLU0_17 ~ dmso48hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3"
)

boxplot(dmso48hr17$RFLUFin_17 ~ dmso48hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 17-3"
)

#DMSO 78-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 5FU Project 78-1",cex = 2,font = 2)

boxplot(dmso72hr78$RFLU0_78 ~ dmso72hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1"
)

boxplot(dmso72hr78$RFLUFin_78 ~ dmso72hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 78-1"
)

#DMSO 75-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 5FU Project 75-1",cex = 2,font = 2)

boxplot(dmso72hr75$RFLU0_75 ~ dmso72hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1"
)

boxplot(dmso72hr75$RFLUFin_75 ~ dmso72hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 75-1"
)

#DMSO 17-3 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 5FU Project 17-3",cex = 2,font = 2)

boxplot(dmso72hr17$RFLU0_17 ~ dmso72hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3"
)

boxplot(dmso72hr17$RFLUFin_17 ~ dmso72hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 17-3"
)
```



Now I'm going to combine these DRCs - hopefully they look okay

```{r Filter Models}
#24hr Timepoint
dox24tox_78 <- doxo24hr78 %>% mu
doxotox <- doxosamples %>% mutate(response = AvgPer*100)
summary(doxotox)

fluotox <- fluosamples %>% mutate(response = AvgPer*100)
summary(fluotox)

dmsotox <- dmsosamples %>% mutate(response = AvgPer*100)
as.vector(dmsotox$response)
summary(dmsotox)
```


```{r DRC Combine}
#24hr Timepoint
plot.new
tuntox_H21792_model <- drm(response~Conc, data = tuntox_H21792, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(tuntox_H21792_model, type = "none", broken = TRUE, 
     xt = c(0.01, 0.1, 0.5, 1, 10, 50, 100), xttrim = FALSE, 
     ylim = c(0,150), cex = 1, col = "#94C47D", lwd = 4, ylab = "Percent Viability (%)", xlab = "Concentration (uM)", main = "TUNICAMYCIN", lty = c(1))

par(new=TRUE)
tuntox_H24280_model <- drm(response~Conc, data = tuntox_H24280, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(tuntox_H24280_model, add = TRUE, col = "#94C47D", lwd = 4, lty = c(6), type = "none")

par(new=TRUE)
tuntox_C40210_model <- drm(response~Conc, data = tuntox_C40210, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(tuntox_C40210_model, add = TRUE, col = "darkgreen", lwd = 4, lty = c(1), type = "none")
legend(x = "bottomleft", legend = c("H21792", "H24280", "C40210", "C40280"), lty = c(1, 6, 1, 6), col = c("#94C47D", "#94C47D","darkgreen", "darkgreen"), lwd = 4)

```

